---
title: "Honours_Project"
format: pdf
editor: visual
---

```{r}
library(igraph)
library(ggraph)
library(ggplot2)
```
# Plotting networks:

```{r}
plotnet <- function(network_generated){
  net <- ggraph(network_generated,layout="fr")+geom_edge_link(alpha=0.5)+geom_node_point(size=1)+theme_void()
  return(net)
}
```

# Functions to generate networks

kbar = 4, 6, 8 10

#### Random network:

```{r}
randgraph <- function(nodes, kbar = NULL) {
  
  p <- kbar / (nodes - 1)
  g <- sample_gnp(nodes, p, directed = FALSE, loops = FALSE)
  return(g)
}

netrand <- randgraph(nodes=2^9,kbar=6)
plotnet(netrand)
edge_density(netrand)
degree_vector <- degree(netrand)     
degree_vector
mean_degree <- mean(degree_vector)  
mean_degree
```

#### Small-world network:

```{r}
#nei=Integer constant, the neighborhood within which the vertices of the lattice will be connected.p=Real constant between zero and one, the rewiring probability(from help function)
smallworldgraph <- function(nodes, kbar = NULL, prob = 0.1) {
  neighbours <- floor(kbar/2)
  swg <- sample_smallworld(dim = 1, size = nodes, nei = neighbours, p = prob)
  return(swg)
}

netsw <- smallworldgraph(nodes=2^9,kbar=10,prob=0.1)
plotnet(netsw)
edge_density(netsw)
degree_vector <- degree(netsw)     
degree_vector
mean_degree <- mean(degree_vector)  
mean_degree
```

#### Scale-free networks:

```{r}
#numeric constant = m (number of edges to add in each time step according to help function)
scalefreegraph <- function(nodes, kbar = NULL) {

  m <-floor(kbar/2)

  sfg <- sample_pa(nodes, m=m, directed = FALSE, zero.appeal = 1)
  
  return(sfg)
}

net <- scalefreegraph(nodes=2^5,kbar=6)
plotnet(net)
edge_density(net)

#testing
degree_vector <- degree(net)     
degree_vector
mean_degree <- mean(degree_vector)  
mean_degree

```
# Performing community detection:

```{r}
louvaincd <- function(network_gen, resolution=1){
  cl <- cluster_louvain(network_gen, resolution=resolution)
  
  return(cl)
}

leidencd <- function(network_gen, resolution=1){
  cl <- cluster_leiden(network_gen, resolution=resolution,objective_function = "modularity")
 
  return(cl)}

```

# Metrics:

## Modularity function: (used from igraph package)

```{r}
modularityll <- function(network_gen, cl_louvain = NULL, cl_leiden = NULL) {
  
  # Compute modularity for Louvain 
  louvain_mod <- if (!is.null(cl_louvain)) modularity(network_gen, membership(cl_louvain)) else NA_real_
  
  # Compute modularity for Leiden 
  leiden_mod  <- if (!is.null(cl_leiden)) modularity(network_gen, membership(cl_leiden)) else NA_real_
  
  data.frame(
    modularity_louvain = louvain_mod,
    modularity_leiden  = leiden_mod,
    stringsAsFactors = FALSE
  )
}

```

## Conductance function:

```{r}

conductance_safe <- function(graph, group) {
  # Return NA if group is empty or the whole graph
  if (length(group) == 0 || length(group) == vcount(graph)) return(NA_real_)
  
  S <- V(graph)[group]
  S_bar <- V(graph)[!V(graph) %in% S]
  
  # Number of edges crossing between S and S_bar
  cut_edges <- ecount(graph) -
               ecount(induced_subgraph(graph, S)) -
               ecount(induced_subgraph(graph, S_bar))
  
  # Volumes (sum of degrees)
  vol_S <- sum(degree(graph, S))
  vol_Sbar <- sum(degree(graph, S_bar))
  
  cut_edges / min(vol_S, vol_Sbar)
}

conductancell <- function(network_gen, cl_louvain = NULL, cl_leiden = NULL) {
  
  safe_cond <- function(cl) {
    if (is.null(cl)) return(NA_real_)
    groups <- split(V(network_gen), membership(cl))
    if (length(groups) <= 1) return(NA_real_)  # skip if only 1 community
    vals <- vapply(groups, function(g) conductance_safe(network_gen, g), numeric(1))
    mean(vals, na.rm = TRUE)
  }
  
  data.frame(
    conductance_louvain = safe_cond(cl_louvain),
    conductance_leiden  = safe_cond(cl_leiden),
    stringsAsFactors = FALSE
  )
}



```

## Stability function:

```{r}

if (!requireNamespace("aricode", quietly = TRUE)) {
  install.packages("aricode")
}
library(aricode)

normalize_membership <- function(mem) {
  as.integer(factor(mem))
}

stability <- function(network_gen, n_runs, compare_method = "nmi", resolution = 1) {

  results <- list()
  
  for (algo in c("louvain", "leiden")) {
    communities <- vector("list", n_runs)
    
    for (i in 1:n_runs) {
      cl_obj <- if (algo == "louvain") {
        louvaincd(network_gen, resolution = resolution)
      } else {
        leidencd(network_gen, resolution = resolution)
      }
      
      # Convert membership to integer labels
      communities[[i]] <- normalize_membership(membership(cl_obj))
    }
    
    similarities <- numeric(0)
    
    for (i in 1:(n_runs - 1)) {
      for (j in (i + 1):n_runs) {
        if (compare_method == "nmi") {
          sim <- aricode::NMI(communities[[i]], communities[[j]])
        } else if (compare_method == "ari") {
          sim <- aricode::ARI(communities[[i]], communities[[j]])
        } else {
          stop("compare_method must be either 'nmi' or 'ari'")
        }
        similarities <- c(similarities, sim)
      }
    }
    
    results[[algo]] <- mean(similarities)
  }
  
  return(c(stability_louvain = results$louvain,
           stability_leiden  = results$leiden))
}

```


SIZES TESTED AT: log_2(Size)

3,4

5,6

7,8

9,10

## PARALLEL VERSIONS:

#### Random network:

```{r}
if (!requireNamespace("future", quietly = TRUE)) {
  install.packages("future")
}
if (!requireNamespace("future.apply", quietly = TRUE)) {
  install.packages("future.apply")
}
library(future)
library(future.apply)

twosizes_random_parallel <- function(sizes = c(10, 15), n_runs = 100, stability_repeats = 100, resolutions = c(1), kbar = 1, workers = availableCores()) {
  
  
  plan(multisession, workers = workers)
  
  
  tasks <- expand.grid(
    size = sizes,
    run  = seq_len(n_runs),
    res  = resolutions,
    stringsAsFactors = FALSE
  )
  
  
  results_list <- future_lapply(seq_len(nrow(tasks)), function(idx) {
    task <- tasks[idx, ]
    size <- task$size
    i    <- task$run
    res  <- task$res
    
    set.seed(i)  
    
    #generate random network
    g <- randgraph(size, kbar)
    
    #community detection
    louvain <- louvaincd(g, resolution = res)
    leiden  <- leidencd(g, resolution = res)
    #metrics
    mods <- modularityll(g, cl_louvain = louvain, cl_leiden = leiden)
    cons <- conductancell(g, cl_louvain = louvain, cl_leiden = leiden)
    stability_vals <- stability(g, n_runs = stability_repeats,resolution=res)
    
  
    data.frame(
      graph_size = size,
      run = i,
      network = "random",
      kbar = kbar,
      resolution = res,
      number_of_communities_louvain = length(unique(membership(louvain))),
      number_of_communities_leiden  = length(unique(membership(leiden))),
      modularity_louvain  = mods$modularity_louvain[1],
      modularity_leiden   = mods$modularity_leiden[1],
      conductance_louvain = cons$conductance_louvain,
      conductance_leiden  = cons$conductance_leiden,
      stability_louvain = stability_vals["stability_louvain"],
      stability_leiden  = stability_vals["stability_leiden"],
      stringsAsFactors = FALSE
    )
    
  }, future.seed = NA)  
  df <- do.call(rbind, results_list)
  
 
  plan(sequential) 
  
  return(df)
}


size_pairs <- list(
  c(16, 32),
  c(64, 128),
  c(256, 512)
)
kbars <- c(4, 6, 8, 10)
resolutions <- seq(0.5, 5, by = 0.5)
n_runs <- 100
stability_repeats <- 50

rds_file <- "res_results_random.rds"
if (file.exists(rds_file)) {
  df_all <- readRDS(rds_file)
} else {
  df_all <- data.frame()
}


for (k in kbars) {
  
  for (pair in size_pairs) {
    
    df_new <- twosizes_random_parallel(
      sizes = pair,
      n_runs = n_runs,
      stability_repeats = stability_repeats,
      resolutions = resolutions,
      kbar = k
    )
  
    df_all <- rbind(df_all, df_new)
    saveRDS(df_all, rds_file)
  }
}

```

#### Small-world network:

```{r}

library(future)
library(future.apply)

twosizes_smallworld_parallel <- function(sizes = c(10, 15), p = 0.1, n_runs = 100, stability_repeats = 100, resolutions = c(1), kbar = 1, workers = availableCores()) {
  
 
  plan(multisession, workers = workers)
  
  
  tasks <- expand.grid(
    size = sizes,
    run  = seq_len(n_runs),
    res  = resolutions,
    stringsAsFactors = FALSE
  )
  

  results_list <- future_lapply(seq_len(nrow(tasks)), function(idx) {
    task <- tasks[idx, ]
    size <- task$size
    i    <- task$run
    res  <- task$res
    
    set.seed(i)  
    
    #generate small-world graph
    g <- smallworldgraph(nodes=size,kbar=kbar, prob=p)
    
    #community detection
    louvain <- louvaincd(g, resolution = res)
    leiden  <- leidencd(g, resolution = res)
    #metrics
    mods <- modularityll(g, cl_louvain = louvain, cl_leiden = leiden)
    cons <- conductancell(g, cl_louvain = louvain, cl_leiden = leiden)
    stability_vals <- stability(g, n_runs = stability_repeats,resolution=res)
    
   
    data.frame(
      graph_size = size,
      run = i,
      network = "Small-world",
      kbar = kbar,
      resolution = res,
      number_of_communities_louvain = length(unique(membership(louvain))),
      number_of_communities_leiden  = length(unique(membership(leiden))),
      modularity_louvain  = mods$modularity_louvain[1],
      modularity_leiden   = mods$modularity_leiden[1],
      conductance_louvain = cons$conductance_louvain,
      conductance_leiden  = cons$conductance_leiden,
      stability_louvain = stability_vals["stability_louvain"],
      stability_leiden  = stability_vals["stability_leiden"],
      stringsAsFactors = FALSE
    )
    
  }, future.seed = NA)  
 
  dfsw <- do.call(rbind, results_list)
  

  plan(sequential)
  
  return(dfsw)
}
size_pairs <- list(
  c(16, 32),
  c(64, 128),
  c(256, 512)
)

kbars <- c(4, 6, 8, 10)
resolutions <- seq(0.5, 5, by = 0.5)
n_runs <- 100
stability_repeats <- 50

rds_file <- "res_results_smallworld.rds"
if (file.exists(rds_file)) {
  df_all <- readRDS(rds_file)
} else {
  df_all <- data.frame()
}


for (k in kbars) {
  for (pair in size_pairs) {
    
    df_new <- twosizes_smallworld_parallel(
      sizes = pair,
      n_runs = n_runs,
      stability_repeats = stability_repeats,
      resolutions = resolutions,
      kbar = k
    )
    df_all <- rbind(df_all, df_new)
    saveRDS(df_all, rds_file)
  }
}
```

#### Scale-free network:

```{r}
library(future.apply)
library(igraph)

twosizes_scalefree_parallel <- function(sizes = c(10, 15), n_runs = 100,
                                        stability_repeats = 50, resolutions = c(1), kbar = 1,
                                        workers = availableCores()) {
  
  plan(multisession, workers = workers)  

  process_graph <- function(size, i, res) {
    set.seed(i)
    #generate scale-free network
    g <- scalefreegraph(size, kbar)
    
    #community detection
    louvain <- louvaincd(g, resolution = res)
    leiden  <- leidencd(g, resolution = res)
    
    #metrics
    mods <- modularityll(g, cl_louvain = louvain, cl_leiden = leiden)
    cons <- conductancell(g, cl_louvain = louvain, cl_leiden = leiden)
    stability_vals <- stability(g, n_runs = stability_repeats,resolution=res)
    
    data.frame(
      graph_size = size,
      run = i,
      network = "Scale-free",
      kbar = kbar,
      resolution = res,
      number_of_communities_louvain = length(unique(membership(louvain))),
      number_of_communities_leiden  = length(unique(membership(leiden))),
      modularity_louvain  = mods$modularity_louvain,
      modularity_leiden   = mods$modularity_leiden,
      conductance_louvain = cons$conductance_louvain,
      conductance_leiden  = cons$conductance_leiden,
      stability_louvain   = stability_vals["stability_louvain"],
      stability_leiden    = stability_vals["stability_leiden"],
      stringsAsFactors = FALSE
    )
  }
  
  
  all_combinations <- expand.grid(size = sizes, run = 1:n_runs, res = resolutions,
                                  stringsAsFactors = FALSE)
  

  dfsf_list <- future.apply::future_lapply(1:nrow(all_combinations), function(idx) {
    row <- all_combinations[idx, ]
    process_graph(row$size, row$run, row$res)
  },
  future.seed = NA )
  
  
  dfsf <- do.call(rbind, dfsf_list)
  
  return(dfsf)
}

size_pairs <- list(
  c(16, 32),
  c(64, 128),
  c(256, 512)
)
kbars <- c(4, 6, 8, 10)
resolutions <- seq(0.5, 5, by = 0.5)
n_runs <- 100
stability_repeats <- 50

rds_file <- "res_results_scale_free.rds"
if (file.exists(rds_file)) {
  df_all <- readRDS(rds_file)
} else {
  df_all <- data.frame()
}


for (k in kbars) {
  
  for (pair in size_pairs) {
    
    df_new <- twosizes_scalefree_parallel(
      sizes = pair,
      n_runs = n_runs,
      stability_repeats = stability_repeats,
      resolutions = resolutions,
      kbar = k
    )
    df_all <- rbind(df_all, df_new)
    saveRDS(df_all, rds_file)
  }
}

```

## Modularity at different densities and sizes:

```{r}
library(dplyr)
library(ggplot2)

modularity_plot <- function(network_type, show_legend = FALSE) {
  # Filter data for the specified network type
  network_data <- dens_size_random|> filter(network == network_type)
  
  df_long <- tidyr::pivot_longer(
    network_data,
    cols = c(modularity_louvain, modularity_leiden),
    names_to = "algorithm", 
    values_to = "modularity"
  )
  
  df_long$algorithm <- gsub("modularity_", "", df_long$algorithm)
  df_long$log2_size <- log2(df_long$graph_size)
  df_long$group <- interaction(df_long$algorithm, df_long$log2_size)
  
  # Define colors for algorithms
  alg_colors <- c("louvain" = "#2A9D8F", "leiden" = "#F8766D")
  
  # Create plot with TWO geom_boxplot layers
  p <- ggplot(df_long, aes(x = log2_size, y = modularity,
                           fill = algorithm, color = algorithm, group = group)) +
    
    geom_boxplot(
      alpha = 0.7,
      position = position_dodge(width = 0.8),
      outlier.shape = NA,  
      median.colour = "black",
      fatten=1
    ) +
   
    geom_boxplot(
      aes(fill = NULL, color = algorithm),  
      position = position_dodge(width = 0.8),
      outlier.shape = 16,
      outlier.size = 1.5,
      outlier.alpha = 0.8,
      fatten = NULL,  
      alpha = 0  
    ) +
    scale_fill_manual(values = alg_colors) +
    scale_color_manual(values = alg_colors) +
    facet_wrap(~ kbar, ncol = 2) +  
    labs(
      title = paste0("Average modularity on a ", network_type, 
                     " network."),
      x = expression(log[2]~"(Graph Size)"),
      x = expression(log[2]~"(Graph Size)"),
      y = "Average modularity",
      fill = "Algorithm",
      color = "Algorithm"
    ) +
    scale_x_continuous(
      breaks = unique(df_long$log2_size),
      labels = function(x) round(x, 1)
    ) +
    theme_minimal(base_size = 14) +
    theme(
      axis.text.x = element_text(angle = 0, hjust = 0.5)
    )
  
  # Remove legend if not specified
  if (!show_legend) {
    p <- p + theme(legend.position = "none")
  } else {
    p <- p + theme(legend.position = "right")
  }
  
  # Save individual plot
  filename <- paste0("modularity_", tolower(gsub(" ", "_", network_type)), ".pdf")
  ggsave(filename, plot = p, width = 12, height = 7)
  
  return(p)
}


random_plot <- modularity_plot("Random", show_legend = TRUE)
#small_world_plot <- modularity_plot("Small-world", show_legend = TRUE)
#scale_free_plot <- modularity_plot("Scale-free", show_legend = TRUE)

print(random_plot)
```

## Conductance at different densites and sizes:

```{r}
library(ggplot2)
library(dplyr)


conductance_plot <- function(network_type, show_legend = FALSE) {
  # Filter data for the specified network type
  network_data <- dens_size_sf |> filter(network == network_type)
  
  df_long <- tidyr::pivot_longer(
    network_data,
    cols = c(conductance_louvain, conductance_leiden),
    names_to = "algorithm",
    values_to = "conductance"  
  )
  
  df_long$algorithm <- gsub("conductance_", "", df_long$algorithm)  #
  df_long$log2_size <- log2(df_long$graph_size)
  df_long$group <- interaction(df_long$algorithm, df_long$log2_size)
  
  # Define colors for algorithms
  alg_colors <- c("louvain" = "#2A9D8F", "leiden" = "#F8766D")
  
  # Create plot with TWO geom_boxplot layers
  p <- ggplot(df_long, aes(x = log2_size, y = conductance,  
                           fill = algorithm, color = algorithm, group = group)) +
   
    geom_boxplot(
      alpha = 0.7,
      position = position_dodge(width = 0.8),
      outlier.shape = NA,  
      median.colour = "black",
      fatten=1
    ) +
   
    geom_boxplot(
      aes(fill = NULL, color = algorithm),  
      position = position_dodge(width = 0.8),
      outlier.shape = 16,
      outlier.size = 1.5,  
      outlier.alpha = 0.8,
      fatten = NULL, 
      alpha = 0 
    ) +
    scale_fill_manual(values = alg_colors) +
    scale_color_manual(values = alg_colors) +
    facet_wrap(~ kbar, ncol = 2) +  
    labs(
      title = paste0("Average conductance on a ", network_type, 
                     " network."),
      x = expression(log[2]~"(Graph Size)"),
      y = "Average conductance",  
      fill = "Algorithm",
      color = "Algorithm"
    ) +
    scale_x_continuous(
      breaks = unique(df_long$log2_size),
      labels = function(x) round(x, 1)
    ) +
    theme_minimal(base_size = 14) +
    theme(
      axis.text.x = element_text(angle = 0, hjust = 0.5)
    )
  
  # Remove legend if not specified
  if (!show_legend) {
    p <- p + theme(legend.position = "none")
  } else {
    p <- p + theme(legend.position = "right")
  }
  
  # Save individual plot
  filename <- paste0("conductance_", tolower(gsub(" ", "_", network_type)), ".pdf")
  ggsave(filename, plot = p, width = 12, height = 7)
  
  return(p)
}


#random_plot <- conductance_plot("Random", show_legend = TRUE)
#small_world_plot <- conductance_plot("Small-world", show_legend = TRUE)
scale_free_plot <- conductance_plot("Scale-free", show_legend = TRUE)

print(small_world_plot)

min(dens_size_sw$stability_louvain)
min(dens_size_sf$conductance_louvain)
```

## Stability at different sizes and densities

```{r}
library(ggplot2)
library(dplyr)

stability_plot <- function(network_type, show_legend = FALSE) {
  # Filter data for the specified network type
  network_data <- dens_size_sf |> filter(network == network_type)
  
  df_long <- tidyr::pivot_longer(
    network_data,
    cols = c(stability_louvain, stability_leiden),  
    names_to = "algorithm",
    values_to = "stability"  
  )
  
  df_long$algorithm <- gsub("stability_", "", df_long$algorithm)  
  df_long$log2_size <- log2(df_long$graph_size)
  df_long$group <- interaction(df_long$algorithm, df_long$log2_size)
  
  # Define colors for algorithms
  alg_colors <- c("louvain" = "#2A9D8F", "leiden" = "#F8766D")
  

  p <- ggplot(df_long, aes(x = log2_size, y = stability,  
                           fill = algorithm, color = algorithm, group = group)) +
  
    geom_boxplot(
      alpha = 0.7,
      position = position_dodge(width = 0.8),
      outlier.shape = NA,  
      median.colour = "black", 
      fatten = 1 
    ) +
  
    geom_boxplot(
      aes(fill = NULL, color = algorithm),  
      position = position_dodge(width = 0.8),
      outlier.shape = 16,
      outlier.size = 1.5,  
      outlier.alpha = 0.8,
      fatten = NULL,  
      alpha = 0  
    ) +
    scale_fill_manual(values = alg_colors) +
    scale_color_manual(values = alg_colors) +
    facet_wrap(~ kbar, ncol = 2) +  
    labs(
      title = paste0("Average stability on a ", network_type, 
                     " network."),
      x = expression(log[2]~"(Graph Size)"),
      y = "Average stability (NMI)",  
      fill = "Algorithm",
      color = "Algorithm"
    ) +
    scale_x_continuous(
      breaks = unique(df_long$log2_size),
      labels = function(x) round(x, 1)
    ) +
    theme_minimal(base_size = 14) +
    theme(
      axis.text.x = element_text(angle = 0, hjust = 0.5)
    )
  
  # Remove legend if not specified
  if (!show_legend) {
    p <- p + theme(legend.position = "none")
  } else {
    p <- p + theme(legend.position = "right")
  }
  
  # Save individual plot
  filename <- paste0("stability_", tolower(gsub(" ", "_", network_type)), ".pdf")
  ggsave(filename, plot = p, width = 12, height = 7)
  
  return(p)
}

#random_plot <- stability_plot("Random", show_legend = TRUE)
#small_world_plot <- stability_plot("Small-world", show_legend = TRUE)
scale_free_plot <- stability_plot("Scale-free", show_legend = TRUE)

print(scale_free_plot)
#print(small_world_plot)
```

# MODULARITY WITH RES AND DENSITY

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)


create_modularity_plot <- function(df_all, kbar_val, network_type) {
  # Filter data
  df_filtered <- df_all |>
    filter(kbar == kbar_val, network == network_type)
 
  # Prepare modularity data
  mod_long <- df_filtered |>
    select(graph_size, resolution, modularity_louvain, modularity_leiden) |>
    pivot_longer(
      cols = starts_with("modularity"),
      names_to = "algorithm",
      values_to = "modularity"
    ) |>
    mutate(
      algorithm = gsub("modularity_", "", algorithm)
    )
  
  # Prepare communities data
  comm_long <- df_filtered |>
    select(graph_size, resolution, number_of_communities_louvain, number_of_communities_leiden) |>
    pivot_longer(
      cols = starts_with("number_of_communities"),
      names_to = "algorithm",
      values_to = "communities"
    ) |>
    mutate(
      algorithm = gsub("number_of_communities_", "", algorithm)
    )
  
  # Join modularity and communities data
  df_combined <- mod_long |>
    left_join(comm_long, by = c("graph_size", "resolution", "algorithm"))
  
  # Summarise
  df_summary <- df_combined |>
    group_by(graph_size, resolution, algorithm) |>
    summarise(
      mean_modularity = mean(modularity),
      mean_communities = mean(communities),
      .groups = "drop"
    )
  
  # Determine if the line is the lowest at each resolution & size
  df_summary <- df_summary |>
    group_by(graph_size, resolution) |>
    mutate(
      is_bottom = mean_modularity == min(mean_modularity)
    ) |>
    ungroup() |>
    mutate(
      algorithm_label = paste0(algorithm, " (modularity)"),
      point_shape = "Average number of communities"
    )
  
  # Plot
  p <- ggplot(df_summary, aes(x = resolution, y = mean_modularity, color = algorithm_label)) +
    geom_line(linewidth = 1, alpha = 0.7, aes(group = algorithm_label)) +
    geom_point(aes(shape = point_shape), size = 2, alpha = 0.7) +
    geom_text(
      aes(
        label = round(mean_communities),
        vjust = ifelse(is_bottom, 1.3, -0.7)
      ),
      hjust = 0.5,
      size = 3.5,
      fontface = "bold",
      show.legend = FALSE
    ) +
    facet_wrap(~ graph_size, nrow = 2) +
    coord_cartesian(clip = "off") +
    scale_shape_manual(
      name = NULL,
      values = c("Average number of communities" = 16)
    ) +
    labs(
      title = paste0("Average modularity on a ", network_type, 
                     " network at a mean degree of ", kbar_val,"."),
      x = "Resolution",
      y = "Average modularity",
      color = "Algorithm"
    ) +
    theme_minimal() +
    theme(
      strip.text = element_text(face = "bold"),
      plot.title = element_text(hjust = 0.5, size = 14),
      plot.subtitle = element_text(hjust = 0.5, size = 10),
      legend.position = "right"
    )
  
  # Save
  filename <- paste0("modularity_", kbar_val, "_", network_type, ".pdf")
  ggsave(filename, plot = p, width = 10, height = 7)
  
  return(p)
}

df_all <- readRDS("res_results_random.rds")
rownames(df_all) <- NULL
plot_0.2 <- create_modularity_plot(df_all,4, "Random")
plot_0.4 <- create_modularity_plot(df_all,6, "Random")
plot_0.6 <- create_modularity_plot(df_all,8, "Random")
plot_0.8 <- create_modularity_plot(df_all,10, "Random")
plot_0.2
plot_0.4
plot_0.6
plot_0.8

df_all <- readRDS("res_results_smallworld.rds")
rownames(df_all) <- NULL

plot_0.2 <- create_modularity_plot(df_all,4, "Small-world")
plot_0.4 <- create_modularity_plot(df_all,6, "Small-world")
plot_0.6 <- create_modularity_plot(df_all,8, "Small-world")
plot_0.8 <- create_modularity_plot(df_all,10, "Small-world")
plot_0.2
plot_0.4
plot_0.6
plot_0.8

df_all <- readRDS("res_results_scale_free.rds")
rownames(df_all) <- NULL
plot_0.2 <- create_modularity_plot(df_all,4, "Scale-free")
plot_0.4 <- create_modularity_plot(df_all,6, "Scale-free")
plot_0.6 <- create_modularity_plot(df_all,8, "Scale-free")
plot_0.8 <- create_modularity_plot(df_all,10, "Scale-free")


```

# CONDUCTANCE

```{r}
create_conductance_plot <- function(df_all, kbar_val, network_type) {
  df_filtered <- df_all |>
    filter(kbar == kbar_val, network == network_type)
  
  conductance_long <- df_filtered |>
    select(graph_size, resolution, conductance_louvain, conductance_leiden) |>
    pivot_longer(cols = starts_with("conductance"), names_to = "algorithm", values_to = "conductance") |>
    mutate(algorithm = gsub("conductance_", "", algorithm))
  
  comm_long <- df_filtered |>
    select(graph_size, resolution, number_of_communities_louvain, number_of_communities_leiden) |>
    pivot_longer(cols = starts_with("number_of_communities"), names_to = "algorithm", values_to = "communities") |>
    mutate(algorithm = gsub("number_of_communities_", "", algorithm))
  
  df_combined <- left_join(conductance_long, comm_long, by = c("graph_size", "resolution", "algorithm"))
  
  df_summary <- df_combined |>
    group_by(graph_size, resolution, algorithm) |>
    summarise(mean_conductance = mean(conductance),
              mean_communities = mean(communities), .groups = "drop") |>
    group_by(graph_size, resolution) |>
    mutate(is_bottom = mean_conductance == min(mean_conductance)) |>
    ungroup() |>
    mutate(
      algorithm_label = paste0(algorithm, " (conductance)"),
      point_shape = "Average number of communities"
    )
  
  p <- ggplot(df_summary, aes(x = resolution, y = mean_conductance, color = algorithm_label)) +
    geom_line(linewidth = 1, alpha = 0.7) +
    geom_point(aes(shape = point_shape), size = 2, alpha = 0.7) +
    geom_text(
      aes(label = round(mean_communities), vjust = ifelse(is_bottom, 1.3, -0.7)),
      hjust = 0.5,
      size = 3.5,
      fontface = "bold",
      show.legend = FALSE
    ) +
    facet_wrap(~ graph_size, nrow = 2) +
    coord_cartesian(clip = "off") +
    scale_shape_manual(name = NULL, values = c("Average number of communities" = 16)) +
    labs(
      title = paste0("Average conductance on a ", network_type, 
                     " network at a mean degree of ", kbar_val,"."),
      x = "Resolution", y = "Average conductance", color = "Algorithm"
    ) +
    theme_minimal() +
    theme(
      strip.text = element_text(face = "bold"),
      plot.title = element_text(hjust = 0.5, size = 14),
      plot.subtitle = element_text(hjust = 0.5, size = 10),
      legend.position = "right"
    )
  
  ggsave(paste0("conductance_", kbar_val, "_", network_type, ".pdf"), plot = p, width = 10, height = 7)
  return(p)
}
df_all <- readRDS("res_results_random.rds")
rownames(df_all) <- NULL

plot_0.2 <- create_conductance_plot(df_all,4, "Random")
plot_0.4 <- create_conductance_plot(df_all,6, "Random")
plot_0.6 <- create_conductance_plot(df_all,8, "Random")
plot_0.8 <- create_conductance_plot(df_all,10, "Random")
plot_0.2
plot_0.4
plot_0.6
plot_0.8

df_all <- readRDS("res_results_smallworld.rds")
rownames(df_all) <- NULL

plot_0.2 <- create_conductance_plot(df_all,4, "Small-world")
plot_0.4 <- create_conductance_plot(df_all,6, "Small-world")
plot_0.6 <- create_conductance_plot(df_all,8, "Small-world")
plot_0.8 <- create_conductance_plot(df_all,10, "Small-world")
plot_0.2
plot_0.4
plot_0.6
plot_0.8

df_all <- readRDS("res_results_scale_free.rds")
rownames(df_all) <- NULL
plot_0.2 <- create_conductance_plot(df_all,4, "Scale-free")
plot_0.4 <- create_conductance_plot(df_all,6, "Scale-free")
plot_0.6 <- create_conductance_plot(df_all,8, "Scale-free")
plot_0.8 <- create_conductance_plot(df_all,10, "Scale-free")



```

# STABILITY

```{r}
library(dplyr)
library(tidyr)

create_stability_plot <- function(df_all, kbar_val, network_type) {
  df_filtered <- df_all |>
    filter(kbar == kbar_val, network == network_type)
  
  stability_long <- df_filtered |>
    select(graph_size, resolution, stability_louvain, stability_leiden) |>
    pivot_longer(cols = starts_with("stability"), names_to = "algorithm", values_to = "stability") |>
    mutate(algorithm = gsub("stability_", "", algorithm))
  
  comm_long <- df_filtered |>
    select(graph_size, resolution, number_of_communities_louvain, number_of_communities_leiden) |>
    pivot_longer(cols = starts_with("number_of_communities"), names_to = "algorithm", values_to = "communities") |>
    mutate(algorithm = gsub("number_of_communities_", "", algorithm))
  
  df_combined <- left_join(stability_long, comm_long, by = c("graph_size", "resolution", "algorithm"))
  
  df_summary <- df_combined |>
    group_by(graph_size, resolution, algorithm) |>
    summarise(mean_stability = mean(stability),
              mean_communities = mean(communities), .groups = "drop") |>
    group_by(graph_size, resolution) |>
    mutate(is_bottom = mean_stability == min(mean_stability)) |>
    ungroup() |>
    mutate(
      algorithm_label = paste0(algorithm, " (stability)"),
      point_shape = "Average number of communities"
    )
  
  p <- ggplot(df_summary, aes(x = resolution, y = mean_stability, color = algorithm_label)) +
    geom_line(linewidth = 1, alpha = 0.7) +
    geom_point(aes(shape = point_shape), size = 2, alpha = 0.7) +
    geom_text(
      aes(label = round(mean_communities), vjust = ifelse(is_bottom, 1.3, -0.7)),
      hjust = 0.5,
      size = 3.5,
      fontface = "bold",
      show.legend = FALSE
    ) +
    facet_wrap(~ graph_size, nrow = 2) +
    coord_cartesian(clip = "off") +
    scale_shape_manual(name = NULL, values = c("Average number of communities" = 16)) +
    labs(
      title = paste0("Average stability on a ", network_type, 
                     " network at a mean degree of ", kbar_val,"."),
      x = "Resolution", y = "Average stability(NMI)", color = "Algorithm"
    ) +
    theme_minimal() +
    theme(
      strip.text = element_text(face = "bold"),
      plot.title = element_text(hjust = 0.5, size = 14),
      plot.subtitle = element_text(hjust = 0.5, size = 10),
      legend.position = "right"
    )
  
  ggsave(paste0("stability_", kbar_val, "_", network_type, ".pdf"), plot = p, width = 10, height = 8)
  return(p)
}


df_all <- readRDS("res_results_random.rds")
rownames(df_all) <- NULL
plot_0.2 <- create_stability_plot (df_all,4, "Random")
plot_0.4 <- create_stability_plot (df_all,6, "Random")
plot_0.6 <- create_stability_plot(df_all,8, "Random")
plot_0.8 <- create_stability_plot(df_all,10, "Random")
plot_0.2
plot_0.4
plot_0.6
plot_0.8

df_all <- readRDS("res_results_smallworld.rds")
rownames(df_all) <- NULL

plot_0.2 <- create_stability_plot(df_all,4, "Small-world")
plot_0.4 <- create_stability_plot(df_all,6, "Small-world")
plot_0.6 <- create_stability_plot(df_all,8, "Small-world")
plot_0.8 <- create_stability_plot(df_all,10, "Small-world")
plot_0.2
plot_0.4
plot_0.6
plot_0.8

df_all <- readRDS("res_results_scale_free.rds")
rownames(df_all) <- NULL
plot_0.2 <- create_stability_plot(df_all,4, "Scale-free")
plot_0.4 <- create_stability_plot(df_all,6, "Scale-free")
plot_0.6 <- create_stability_plot(df_all,8, "Scale-free")
plot_0.8 <- create_stability_plot(df_all,10, "Scale-free")



```
